Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-08-16 Masterarbeit_Robotik_Pamuk.tex
change color

\bigskip \noindent \textcolor{red}{Asymmetric Scheduling and Load Balancing for Real-Time on Linux SMP
	Authors: Eric Piel, Philippe Marquet, Julien Soula, and Jean-Luc Dekeyser12
	The paper presents ARTiS, a real-time extension of the GNU/Linux scheduler designed for SMP (Symmetric Multi-Processors) systems3. ARTiS aims to guarantee the preemption of processors for real-time tasks by assigning specific processors to these tasks4. This system ensures low latency by migrating non-preemptible tasks away from real-time processors5. ARTiS also incorporates load-balancing strategies to fully utilize SMP systems without wasting resources. The implementation of ARTiS involves modifications to the Linux scheduler, resulting in significant improvements in latency compared to the standard Linux scheduler6. The paper details the performance evaluation of ARTiS, highlighting its ability to maintain low interrupt latency even under high system load, making it suitable for hard real-time applications. The authors propose further enhancements, including the integration of real-time scheduling policies like EDF (Earliest Deadline First) and RM (Rate Monotonic)7.}

@@

\bigskip \noindent \textcolor{red}{“Testing the limits of general-purpose hypervisors for real-time control systems” by Rui Queiroz, Tiago J. Cruz, and Paulo Simões from the University of Coimbra:
	With the advent of Industry 4.0, there is a growing need for flexibility, security, and resilience in industrial automation infrastructures while maintaining real-time requirements. This paper explores the feasibility of using general-purpose off-the-shelf hypervisors to virtualize cyber-physical systems’ servers and control devices. The authors, Rui Queiroz, Tiago J. Cruz, and Paulo Simões, present an empirical evaluation of these hypervisors, focusing on their ability to handle real-time workloads. The study highlights the challenges posed by the need for determinism and low latency, which are often compromised by hypervisors designed to maximize throughput. The paper concludes that while some hypervisors can manage typical real-time workloads, this capability is not universal across all types of real-time systems. The research underscores the importance of understanding the limits and capabilities of conventional hypervisors to ensure they meet the specific requirements of industrial automation control systems.}

\bigskip \noindent \textcolor{red}{Title: A State-of-the-Art Survey on Real-Time Issues in Embedded Systems Virtualization
	Authors: Zonghua Gu and Qingling Zhao
	Summary: This paper provides a comprehensive survey on real-time issues in virtualization for embedded systems, authored by Zonghua Gu and Qingling Zhao. Virtualization, widely accepted in server and cloud computing, has been increasingly applied to embedded systems with stringent timing constraints. The paper discusses various virtualization systems, including KVM, Xen, and L4, and their applications in embedded systems such as avionics, industrial automation, and mobile phones. It highlights the importance of real-time performance, security, and dependability in these systems. The survey covers different types of virtualization, including Type-1 (bare-metal) and Type-2 (hosted) virtualization, as well as full and para-virtualization. It also addresses specific real-time issues like scheduling, partitioning, and the Lock-Holder Preemption problem. The paper concludes with a discussion on the future directions and challenges in the field of real-time virtualization for embedded systems.}

@@

\bigskip \noindent \textcolor{red}{“Real Time Operating Systems: A Complete Overview” by Mrinal Parikshit Chandane:
	The paper “Real Time Operating Systems: A Complete Overview” by Mrinal Parikshit Chandane provides an in-depth examination of Real Time Operating Systems (RTOS) and their critical role in embedded systems, particularly in telecommunication applications such as telephony, navigation, and military signaling systems. RTOS is essential for applications that require strict deadline constraints and the ability to handle multiple tasks simultaneously1. The paper highlights the key features of RTOS, including timing considerations, task prioritization, and communication and synchronization between tasks2.
	The document delves into various design aspects necessary for developing an RTOS, such as task management, multitasking, context switching, task priority, and kernel functions3. It explains how tasks are created, prioritized, and managed within an RTOS, emphasizing the importance of efficient CPU utilization and the prevention of data corruption through mutual exclusion. The paper also discusses the implementation of RTOS, covering topics like programming language selection, task stack management, and the initialization process.
	Furthermore, the paper presents a practical example of designing and implementing an RTOS for a Philips 8052 microcontroller, demonstrating the application of theoretical concepts in real-world scenarios. The successful implementation of applications such as a column controller, digital calculator, and dancing LEDs showcases the versatility and effectiveness of RTOS in managing complex embedded systems4.
	Overall, the paper provides a comprehensive overview of RTOS, offering valuable insights into its architecture, design, and implementation, making it a significant contribution to the field of embedded systems5.}

\bigskip \noindent \textcolor{red}{The paper “Challenges in Real-Time Virtualization and Predictable Cloud Computing” explores the integration of real-time systems with cloud computing and virtualization technologies. The authors, Marisol García-Valls, Tommaso Cucinotta, and Chenyang Lu, identify the significant technical challenges in supporting real-time applications within cloud environments1. They highlight that while cloud computing offers benefits such as reduced operational costs, server consolidation, and elastic resource provisioning, it struggles to meet the demands of soft real-time applications like online video streaming, cloud-based gaming, and telecommunication management2. These applications require predictable performance in open, shared, and virtualized environments3.
	The paper discusses the evolution of cloud computing, emphasizing the shift from local computing resources to distributed cloud-based models. It outlines the benefits of virtualization, including functional execution isolation, easier management, and the coexistence of legacy and new applications4. However, the authors note that the multi-tenant nature of cloud computing introduces challenges in providing stable and predictable performance due to resource sharing among multiple virtual machines (VMs).
	The authors delve into various virtualization techniques, such as full virtualization, hardware-assisted virtualization, para-virtualization, OS-level virtualization, and application-level virtualization, each with its performance characteristics and suitability for real-time applications. They also address the importance of real-time scheduling and resource management in virtualized environments, highlighting the need for hierarchical scheduling and the role of real-time hypervisors.
	The paper concludes by presenting potential future research directions to enhance the predictability and performance of cloud-based real-time applications, emphasizing the need for improved resource management frameworks and real-time virtualization techniques.}

@@

\bigskip \noindent \textcolor{red}{Title: Hard Real Time Linux* Using Xenomai* on Intel® Multi-Core Processors12
	Author: Amarpreet Singh Ugal, BIOS/Firmware Engineer, Intel Corporation
	Summary: This document explores the implementation of hard real-time capabilities in Linux using Xenomai on Intel® multi-core processors. Traditional Linux is not a hard real-time operating system because it cannot guarantee that tasks will meet strict deadlines34. To address this, the document discusses the use of a high-priority real-time kernel that runs between the hardware and standard Linux. This real-time kernel executes real-time tasks and suspends normal Linux processes during this period56. The real-time scheduler treats the standard Linux kernel as an idle task, allowing real-time tasks to preempt normal processes78. Xenomai, which uses an interrupt pipeline from the ADEOS project, is highlighted as a solution for managing interrupts and ensuring minimal latency and jitter. The document also covers the installation and configuration of Xenomai on CentOS 5.2, including kernel patching and testing with various tools like switchbench, switchtest, cyclictest, clocktest, and latency. The detailed steps and configurations provided aim to help developers achieve hard real-time performance on Intel® Core™ i7 multi-core processors.}

@@

\bigskip \noindent \textcolor{red}{Title: The Real-Time Linux Kernel: A Survey on PREEMPT\_RT12
	Authors: Federico Reghenzani, Giuseppe Massari, and William Fornaciari from Politecnico di Milano3
	Summary: This survey explores the evolution and current state of the PREEMPT\_RT patch for the Linux kernel, which aims to enhance the real-time capabilities of Linux. The authors discuss the increasing demand for real-time applications and the challenges posed by using Commercial-Off-The-Shelf (COTS) hardware in such environments. The PREEMPT\_RT patch modifies the existing Linux kernel to improve predictability and reduce latencies, making it suitable for real-time applications. The survey covers various approaches to real-time Linux, including cokernel approaches like RTLinux, Xenomai, and RTAI, and compares them with the PREEMPT\_RT patch4. The authors highlight the benefits of using Linux in real-time systems, such as the availability of rich hardware support and a well-established programming environment. They also discuss the challenges of integrating real-time capabilities into a general-purpose operating system and the ongoing efforts to address these issues. The survey concludes with an overview of industrial and scientific use cases that have benefited from the PREEMPT\_RT patch, emphasizing its significance in fields like aerospace, automotive, and high-performance computing.}

\bigskip \noindent \textcolor{red}{The paper titled “Performance Evaluation of Xenomai 3” by Ching-Chun (Jim) Huang, Chan-Hsiang Lin, and Che-Kang Wu, presents an in-depth analysis of Xenomai 3, a real-time framework for Linux. Xenomai 3 operates either as a dual-kernel system alongside Linux or natively over mainline Linux kernels, enhanced by PREEMPT RT for stricter response times1. The study evaluates Xenomai 3’s performance, particularly in dual-kernel configuration, using ARM Cortex-A series benchmarks. The authors highlight Xenomai 3’s optimizations in RTOS API emulation, thread-to-thread communications, and reduced overhead. The paper compares Xenomai 3 with its predecessor, Xenomai 2, and the PREEMPT RT-enhanced Linux kernel, demonstrating superior maximum response times to external interrupts in dual-kernel setups. The study employs BeagleBone Black hardware and various kernel configurations to measure latencies under idle and CPU-stressed conditions2. Results indicate that Xenomai 3 generally outperforms Xenomai 2 and PREEMPT RT, except for a slight degradation in timer-IRQ latency under stress. The paper concludes that Xenomai 3 offers significant improvements in real-time performance and flexibility, making it a robust choice for real-time applications.}

>>>>

\bigskip \noindent \textcolor{orange}{Asymmetric Scheduling and Load Balancing for Real-Time on Linux SMP
	Authors: Eric Piel, Philippe Marquet, Julien Soula, and Jean-Luc Dekeyser12
	The paper presents ARTiS, a real-time extension of the GNU/Linux scheduler designed for SMP (Symmetric Multi-Processors) systems3. ARTiS aims to guarantee the preemption of processors for real-time tasks by assigning specific processors to these tasks4. This system ensures low latency by migrating non-preemptible tasks away from real-time processors5. ARTiS also incorporates load-balancing strategies to fully utilize SMP systems without wasting resources. The implementation of ARTiS involves modifications to the Linux scheduler, resulting in significant improvements in latency compared to the standard Linux scheduler6. The paper details the performance evaluation of ARTiS, highlighting its ability to maintain low interrupt latency even under high system load, making it suitable for hard real-time applications. The authors propose further enhancements, including the integration of real-time scheduling policies like EDF (Earliest Deadline First) and RM (Rate Monotonic)7.}

@@

@@

\bigskip \noindent \textcolor{orange}{“Real Time Operating Systems: A Complete Overview” by Mrinal Parikshit Chandane:
	The paper “Real Time Operating Systems: A Complete Overview” by Mrinal Parikshit Chandane provides an in-depth examination of Real Time Operating Systems (RTOS) and their critical role in embedded systems, particularly in telecommunication applications such as telephony, navigation, and military signaling systems. RTOS is essential for applications that require strict deadline constraints and the ability to handle multiple tasks simultaneously1. The paper highlights the key features of RTOS, including timing considerations, task prioritization, and communication and synchronization between tasks2.
	The document delves into various design aspects necessary for developing an RTOS, such as task management, multitasking, context switching, task priority, and kernel functions3. It explains how tasks are created, prioritized, and managed within an RTOS, emphasizing the importance of efficient CPU utilization and the prevention of data corruption through mutual exclusion. The paper also discusses the implementation of RTOS, covering topics like programming language selection, task stack management, and the initialization process.
	Furthermore, the paper presents a practical example of designing and implementing an RTOS for a Philips 8052 microcontroller, demonstrating the application of theoretical concepts in real-world scenarios. The successful implementation of applications such as a column controller, digital calculator, and dancing LEDs showcases the versatility and effectiveness of RTOS in managing complex embedded systems4.
	Overall, the paper provides a comprehensive overview of RTOS, offering valuable insights into its architecture, design, and implementation, making it a significant contribution to the field of embedded systems5.}

@@

\bigskip \noindent \textcolor{orange}{Title: Hard Real Time Linux* Using Xenomai* on Intel® Multi-Core Processors12
	Author: Amarpreet Singh Ugal, BIOS/Firmware Engineer, Intel Corporation
	Summary: This document explores the implementation of hard real-time capabilities in Linux using Xenomai on Intel® multi-core processors. Traditional Linux is not a hard real-time operating system because it cannot guarantee that tasks will meet strict deadlines34. To address this, the document discusses the use of a high-priority real-time kernel that runs between the hardware and standard Linux. This real-time kernel executes real-time tasks and suspends normal Linux processes during this period56. The real-time scheduler treats the standard Linux kernel as an idle task, allowing real-time tasks to preempt normal processes78. Xenomai, which uses an interrupt pipeline from the ADEOS project, is highlighted as a solution for managing interrupts and ensuring minimal latency and jitter. The document also covers the installation and configuration of Xenomai on CentOS 5.2, including kernel patching and testing with various tools like switchbench, switchtest, cyclictest, clocktest, and latency. The detailed steps and configurations provided aim to help developers achieve hard real-time performance on Intel® Core™ i7 multi-core processors.}

@@

\bigskip \noindent \textcolor{green}{Title: The Real-Time Linux Kernel: A Survey on PREEMPT\_RT12
	Authors: Federico Reghenzani, Giuseppe Massari, and William Fornaciari from Politecnico di Milano3
	Summary: This survey explores the evolution and current state of the PREEMPT\_RT patch for the Linux kernel, which aims to enhance the real-time capabilities of Linux. The authors discuss the increasing demand for real-time applications and the challenges posed by using Commercial-Off-The-Shelf (COTS) hardware in such environments. The PREEMPT\_RT patch modifies the existing Linux kernel to improve predictability and reduce latencies, making it suitable for real-time applications. The survey covers various approaches to real-time Linux, including cokernel approaches like RTLinux, Xenomai, and RTAI, and compares them with the PREEMPT\_RT patch4. The authors highlight the benefits of using Linux in real-time systems, such as the availability of rich hardware support and a well-established programming environment. They also discuss the challenges of integrating real-time capabilities into a general-purpose operating system and the ongoing efforts to address these issues. The survey concludes with an overview of industrial and scientific use cases that have benefited from the PREEMPT\_RT patch, emphasizing its significance in fields like aerospace, automotive, and high-performance computing.}

\bigskip \noindent \textcolor{orange}{The paper titled “Performance Evaluation of Xenomai 3” by Ching-Chun (Jim) Huang, Chan-Hsiang Lin, and Che-Kang Wu, presents an in-depth analysis of Xenomai 3, a real-time framework for Linux. Xenomai 3 operates either as a dual-kernel system alongside Linux or natively over mainline Linux kernels, enhanced by PREEMPT RT for stricter response times1. The study evaluates Xenomai 3’s performance, particularly in dual-kernel configuration, using ARM Cortex-A series benchmarks. The authors highlight Xenomai 3’s optimizations in RTOS API emulation, thread-to-thread communications, and reduced overhead. The paper compares Xenomai 3 with its predecessor, Xenomai 2, and the PREEMPT RT-enhanced Linux kernel, demonstrating superior maximum response times to external interrupts in dual-kernel setups. The study employs BeagleBone Black hardware and various kernel configurations to measure latencies under idle and CPU-stressed conditions2. Results indicate that Xenomai 3 generally outperforms Xenomai 2 and PREEMPT RT, except for a slight degradation in timer-IRQ latency under stress. The paper concludes that Xenomai 3 offers significant improvements in real-time performance and flexibility, making it a robust choice for real-time applications.}
